Supplement to: Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-18 supplement.tex
Fiddling and manually merging
Added examples of new primitives

\begin{figure}
  \centering
  \begin{minipage}{0.5\textwidth}    
    \begin{algorithm}[H]
       \caption{Generative model over programs}
       \label{programGenerativeModel}
       \begin{algorithmic}
    %%      \STATE \textbf{function} sampleProgramFromDSL$(\mathcal{D}, \theta, \tau)$:
    %%   \STATE {\bfseries Input:} DSL $\mathcal{D}$, weight vector $\theta$, type $\tau$
    %%   \STATE \textbf{Output:} a program whose type unifies with $\tau$
    %%   \STATE \textbf{return} sample$(\mathcal{D}, \theta, \varnothing, \tau)$
    %% \STATE
         \STATE \textbf{function} sample$(\mathcal{D}, \theta, \mathcal{E}, \tau)$:
      \STATE {\bfseries Input:} DSL $(\mathcal{D},\theta)$, environment $\mathcal{E}$, type $\tau$
      \STATE \textbf{Output:} a program whose type unifies with $\tau$
      \IF{$\tau = \alpha\to\beta$}
      \STATE var $\gets$ an unused variable name
      \STATE body $\sim$ sample$(\mathcal{D},\theta,\{\text{var}:\alpha\}\cup\mathcal{E},\beta)$
       \STATE \textbf{return} \code{(lambda (}var\code{) }body\code{)}
       \ENDIF
       %   \ELSE
       \STATE $\text{primitives} \gets\{p | p: \tau' \in \mathcal{D}\cup\mathcal{E}$ \\
          \hspace*{6.9em}$\text{if }\tau\text{ can unify with yield}(\tau') \} $

@@

@@

\setcounter{algorithm}{2} % there are two algorithms in the main paper.
\begin{algorithm}[hb]
   \caption{DSL Induction Algorithm}
   \label{grammarInductionAlgorithm}
   \begin{algorithmic}
     \STATE {\bfseries Input:} Set of frontiers $\{\mathcal{F}_x\}$
     \STATE \textbf{Hyperparameters:} Pseudocounts $\alpha$, regularization parameter $\lambda$
     \STATE \textbf{Output:} DSL $\mathcal{D}$, weight vector $\theta$
     \STATE Define $L(\mathcal{D},\theta) =  \prod_x \sum_{p\in \mathcal{F}_x} \probability[p|\mathcal{D},\theta]$
     \STATE Define $\theta^*(\mathcal{D}) = \argmax_\theta \text{Dir}(\theta|\alpha) L(\mathcal{D},\theta)$
     \STATE Define $\text{score}(\mathcal{D}) = \log \probability[\mathcal{D}] + L(\mathcal{D},\theta^*) - \|\theta\|_0$
     \STATE $\mathcal{D}\gets$ every primitive in $\{\mathcal{F}_x\}$
     \WHILE {true}
     \STATE N $\gets \{\mathcal{D}\cup \{s\} | x\in X, p\in \mathcal{F}_x, s\text{ a fragment  of }p\}$
     \STATE $\mathcal{D}'\gets \argmax_{\mathcal{D}'\in N}\text{score}(\mathcal{D}') $
     \STATE \textbf{if }$\text{score}(\mathcal{D}') < \text{score}(\mathcal{D})$\textbf{ return }$\mathcal{D},\theta^*(\mathcal{D})$
     \STATE $\mathcal{D}\gets\mathcal{D}'$
     \ENDWHILE
   \end{algorithmic}
\end{algorithm}

@@

>>>>

@@

\begin{figure}[H]
  \centering
  \begin{minipage}{0.5\textwidth}    
    \begin{algorithm}[H]
       \caption{Generative model over programs}
       \label{programGenerativeModel}
       \begin{algorithmic}
    %%      \STATE \textbf{function} sampleProgramFromDSL$(\mathcal{D}, \theta, \tau)$:
    %%   \STATE {\bfseries Input:} DSL $\mathcal{D}$, weight vector $\theta$, type $\tau$
    %%   \STATE \textbf{Output:} a program whose type unifies with $\tau$
    %%   \STATE \textbf{return} sample$(\mathcal{D}, \theta, \varnothing, \tau)$
    %% \STATE
         \STATE \textbf{function} sample$(\mathcal{D}, \theta, \mathcal{E}, \tau)$:
      \STATE {\bfseries Input:} DSL $(\mathcal{D},\theta)$, environment $\mathcal{E}$, type $\tau$
      \STATE \textbf{Output:} a program whose type unifies with $\tau$
      \IF{$\tau = \alpha\to\beta$}
      \STATE var $\gets$ an unused variable name
      \STATE body $\sim$ sample$(\mathcal{D},\theta,\{\text{var}:\alpha\}\cup\mathcal{E},\beta)$
       \STATE \textbf{return} \code{(lambda (}var\code{) }body\code{)}
       \ENDIF
       %   \ELSE
       \STATE $\text{primitives} \gets\{p | p: \tau' \in \mathcal{D}\cup\mathcal{E}$ \\
          \hspace*{6.9em}$\text{if }\tau\text{ can unify with yield}(\tau') \} $

@@

\begin{figure}[H]
  \centering
  \begin{minipage}{0.675\textwidth}    
    \begin{algorithm}[H]
    \setcounter{algorithm}{2} % there are two algorithms in the main paper.
       \caption{DSL Induction Algorithm}
       \label{grammarInductionAlgorithm}
       \begin{algorithmic}
         \STATE {\bfseries Input:} Set of frontiers $\{\mathcal{F}_x\}$
         \STATE \textbf{Hyperparameters:} Pseudocounts $\alpha$, regularization parameter $\lambda$
         \STATE \textbf{Output:} DSL $\mathcal{D}$, weight vector $\theta$
         \STATE Define $L(\mathcal{D},\theta) =  \prod_x \sum_{p\in \mathcal{F}_x} \probability[p|\mathcal{D},\theta]$
         \STATE Define $\theta^*(\mathcal{D}) = \argmax_\theta \text{Dir}(\theta|\alpha) L(\mathcal{D},\theta)$
         \STATE Define $\text{score}(\mathcal{D}) = \log \probability[\mathcal{D}] + L(\mathcal{D},\theta^*) - \|\theta\|_0$
         \STATE $\mathcal{D}\gets$ every primitive in $\{\mathcal{F}_x\}$
         \WHILE {true}
         \STATE N $\gets \{\mathcal{D}\cup \{s\} | x\in X, p\in \mathcal{F}_x, s\text{ a fragment  of }p\}$
         \STATE $\mathcal{D}'\gets \argmax_{\mathcal{D}'\in N}\text{score}(\mathcal{D}') $
         \STATE \textbf{if }$\text{score}(\mathcal{D}') < \text{score}(\mathcal{D})$\textbf{ return }$\mathcal{D},\theta^*(\mathcal{D})$
         \STATE $\mathcal{D}\gets\mathcal{D}'$
         \ENDWHILE
       \end{algorithmic}
    \end{algorithm}
  \end{minipage}
\end{figure}

@@

\subsection{Geometry}
\begin{lstlisting}
#(var_half var_name)
#(var_double var_name)
#(var_next #(var_half var_name))
#(concat (turn (just #(var_half var_name))))
#(@$\lambda$@ (integrate nothing $0 nothing nothing))
#(@$\lambda$@ (integrate $0 true nothing (just var_name)))
#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1)))))
#(integrate (just #(var_half var_name)) true nothing nothing)
#(#(@$\lambda$@ (integrate $0 true nothing (just var_name))) nothing)
#(@$\lambda$@ (concat $0 (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true)))
#(@$\lambda$@ (@$\lambda$@ (integrate (just #(var_double var_name)) true $0 (just $1))))
#(@$\lambda$@ (concat (turn $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true)))
#(@$\lambda$@ (concat $0 (#(@$\lambda$@ (integrate $0 true nothing (just var_name))) nothing)))
#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2)))))
#(#(@$\lambda$@ (concat (turn $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))) nothing)
#(#(@$\lambda$@ (integrate $0 true nothing (just var_name))) (just (var_half #(var_half var_name))))
#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing $0)))
#(concat #(#(@$\lambda$@ (integrate $0 true nothing (just var_name))) (just (var_half #(var_half var_name)))))
#(@$\lambda$@ (#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing $0))) (embed $0)))
#(@$\lambda$@ (repeat nothing (repeat nothing (concat (embed $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) false)))))
#(embed (#(@$\lambda$@ (concat (turn $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))) (just #(var_half var_name))))
#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (turn $0) nothing nothing))
#(@$\lambda$@ (#(@$\lambda$@ (concat $0 (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))) (integrate $0 false nothing nothing)))
#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (concat (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) $0) (integrate $1 true $2 (just var_unit))))))
#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) $0 (embed (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))))
#(#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (concat (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) $0) (integrate $1 true $2 (just var_unit)))))) nothing)
#(@$\lambda$@ (concat (concat (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true) (turn nothing)) (integrate (just $0) true nothing nothing)))
#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (turn nothing) nothing $0)))
#(#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (turn nothing) nothing $0))) nothing)
#(#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (integrate nothing true nothing (just #(var_half var_name))) nothing)
#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (integrate nothing $0 nothing $1) $2 nothing))))
#(@$\lambda$@ (@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing (concat (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) $0) $1)))))
#(#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) false) (just var_name) nothing)
#(#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (turn nothing) nothing $0))) (just #(var_half var_name)))
#(#(@$\lambda$@ (concat $0 (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))) #(#(@$\lambda$@ (integrate $0 true nothing (just var_name))) (just (var_half #(var_half var_name)))))
#(@$\lambda$@ (#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (turn nothing) nothing $0))) (just (var_double $0))))
#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (define #(var_half var_name)) (just #(var_half var_name)) $0)))
#(#(@$\lambda$@ (repeat nothing (repeat nothing (concat (embed $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) false))))) (#(@$\lambda$@ (integrate $0 true nothing (just var_name))) nothing))
#(@$\lambda$@ (#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing $0))) (concat (define $0) #(integrate (just #(var_half var_name)) true nothing nothing))))
#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (concat (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) $0) (integrate $1 true $2 (just var_unit)))))) nothing (just (var_half $0)) false)))
#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) $0 #(embed (#(@$\lambda$@ (concat (turn $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))) (just #(var_half var_name))))))
#(@$\lambda$@ (#(@$\lambda$@ (#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing $0))) (embed $0))) (#(@$\lambda$@ (integrate $0 true nothing (just var_name))) (just $0))))
#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing (#(@$\lambda$@ (repeat nothing (repeat nothing (concat (embed $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) false))))) $0)))
#(embed (#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) $0 #(embed (#(@$\lambda$@ (concat (turn $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))) (just #(var_half var_name)))))) nothing))
#(@$\lambda$@ (concat (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true) (#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) $0 (embed (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true)))) $0)))
#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (integrate nothing $0 nothing $1) $2 nothing)))) (just #(var_half var_name)) (just $0) true))
#(@$\lambda$@ (#(@$\lambda$@ (repeat nothing (repeat nothing (concat (embed $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) false))))) (#(@$\lambda$@ (concat (turn $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))) $0)))
#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) $0 (#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (turn nothing) nothing $0))) nothing)))
#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) $0 (#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (turn $0) nothing nothing)) (just #(var_half var_name)))))
#(#(@$\lambda$@ (@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing (concat (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) $0) $1))))) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) false) true)
#(repeat nothing (#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (concat (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) $0) (integrate $1 true $2 (just var_unit)))))) nothing (just (var_half $0)) false))) #(var_half var_name)))
#(#(@$\lambda$@ (@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing (concat (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) $0) $1))))) (#(@$\lambda$@ (integrate $0 true nothing (just var_name))) nothing) false)
#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) (#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) $0 (embed (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true)))) nothing) (just $0) nothing))
#(@$\lambda$@ (#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing (#(@$\lambda$@ (repeat nothing (repeat nothing (concat (embed $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) false))))) $0))) (#(@$\lambda$@ (concat (turn $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))) $0)))
#(@$\lambda$@ (#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing $0))) (#(@$\lambda$@ (@$\lambda$@ (@$\lambda$@ (repeat nothing (concat (integrate $0 true nothing $1) $2))))) #(#(@$\lambda$@ (concat (turn $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))) nothing) nothing $0)))
#(repeat nothing (concat #(#(@$\lambda$@ (repeat nothing (repeat nothing (concat (embed $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) false))))) (#(@$\lambda$@ (integrate $0 true nothing (just var_name))) nothing)) #(#(@$\lambda$@ (integrate $0 true nothing (just var_name))) (just (var_half #(var_half var_name))))))
#(@$\lambda$@ (repeat (just $0) #(repeat nothing (concat #(#(@$\lambda$@ (repeat nothing (repeat nothing (concat (embed $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) false))))) (#(@$\lambda$@ (integrate $0 true nothing (just var_name))) nothing)) #(#(@$\lambda$@ (integrate $0 true nothing (just var_name))) (just (var_half #(var_half var_name))))))))
#(@$\lambda$@ (#(@$\lambda$@ (#(@$\lambda$@ (repeat nothing (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) nothing $0))) (embed $0))) (#(@$\lambda$@ (#(@$\lambda$@ (@$\lambda$@ (repeat nothing (concat $0 (turn $1))))) $0 #(embed (#(@$\lambda$@ (concat (turn $0) (#(@$\lambda$@ (integrate nothing $0 nothing nothing)) true))) (just #(var_half var_name)))))) (just $0))))
\end{lstlisting}
